Rising from the Ashes II.: something something

### 2024-09-02 paper/ms.tex
Add conclusions

>>>>

\section{Conclusions}\label{sec:conc}
In this work, we examined a specific subhalo in Illustris TNG50. This subhalo is at a Milky Way-progenitor mass at high-$z$ ($z\sim2$). After applying a post-processing step that increased the \MgFe{} of star particles formed before $z=1.5$, this subhalo hosts a strong bimodality in the plane of \MgFe{} and \FeH{}, shown in Figure~\ref{fig:fig1}. This post-processing is justified by arguing that the SFE of dense gas is too low in TNG (Section~\ref{ssec:sfe}).

This bimodality can be traced to an event that occurred at an age of $10.75\,\Gyr$, or formation time of $\sim3\,\Gyr$ ($z\sim2$). Shown as a vertical dashed line in Figure~\ref{fig:alpha}, star particles which form before this form at high-$\alpha$ while stars which form after form at lower $\alpha$. At the dashed line, there is a gap. We argue that the presence of this gap is responsible for the valley in the bimodality (Figure~\ref{fig:fig1}). It is accompanied by a global reduction in the SFR by about a factor of 6 (upper panel of Figure~\ref{fig:history}).

The reduction in the SFR has two effects. First, a lower production of Mg is the natural result of a lack of Type~II SNe. Second, the lack of SF means that stars at \MgFe{} intermediate between the high- and low-$\alpha$ sequences never form. This is the same argument that was first presented in \citet{2024arXiv240707985B}. When observational errors are added to the subhalo's abundance vs age distribution, we show that it is broadly consistent with the Milky Way's distribution (Section~\ref{ssec:compare_obs}).

This work adds further support that the argument made in \citet{2024arXiv240707985B} is a plausible explanation for the Milky Way's abundance bimodality.
